---
title: "Reliability Analysis"
output: 
  flexdashboard::flex_dashboard:
    #theme: bootstrap
    #theme: cerulean
    theme: flatly
    #theme: united
    #theme: simplex
    #theme: yeti
    logo: R_logo.png
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(DT)
library(psych)
library(rstatix)
library(corrr)
library(tigerstats)
library(skimr)
```

```{r Učitavanje podataka iz CSV datoteke}

data <- read.table(file.choose(),                  
                   header = TRUE,                      
                   dec = ",",                          
                   sep = ";",                          
                   stringsAsFactors = TRUE,
                   row.names = 1)

#saveRDS(data, file = "MUHCS20m.RData") 
#head(data)
```

```{r Selekcija varijabli}
#my_data <- data %>% select_if(is.numeric)

#my_data <- data %>% select(FEDSM1, FEDSM2, FEDSM3)
#my_data <- data %>% select(BFPTAP1, BFPTAP2, BFPTAP3)
#my_data <- data %>% select(FLPRR1,	FLPRR2,	FLPRR3)
my_data <- data %>% select(AGKUS1, AGKUS2, AGKUS3)
```

```{r}
n <- nrow(my_data)                                  
m <- ncol(my_data)
summary <- skim(data)
Z <- round(scale(my_data), digits = 3)
```

```{r}
X <- as.matrix(my_data)                    
i <- rep(c(1), times=m)                     
Xs <- X %*% i                               
Xas <- Xs/m                                 
colnames(Xs) <- c("X-sum")
colnames(Xas) <- c("X-mean")
Xas <- as.data.frame(Xas)
```

```{r}
Zm <- as.matrix(Z)                    
Zs <- Zm %*% i                               
Zas <- Zs/m                                 
colnames(Zs) <- c("Z-sum")
colnames(Zas) <- c("Z-mean")
Zas <- as.data.frame(Zas)
```

```{r}
k <- principal(X, nfactors=1, scores=TRUE)   
lamda1 <- k$values[1]                         
K1 <- k$scores
K1<- as.data.frame(K1)
```

```{r}
ds <- describe(my_data, type=2)
ds <- ds[c(3,5,4,8,9,10,11,12)]
colnames(ds) <- c("Mean", "Median", "St.dev", "Min", "Max", "Range", "Skew", "Kurt")
ds <- round(ds, digits = 3)
```

```{r}
RP <- corr.test(my_data)
R <- RP$r
P <- RP$p
```

```{r}
svar <- sum(ds[,3]*ds[,3]) 
varXs <- var(Xs)                             
varZs <- var(Zs)                             

Cronbach <- m/(m-1)*(1-svar/varXs)             
SB <- m/(m-1)*(1-m/varZs)                
KC <- m/(m-1)*(1-1/lamda1)               
k <- (m*m-m)/2                              
AIC<- c((sum(R)-m)/2)/k
K_data <- cbind.data.frame(Xas, Zas, K1)
```


Data
=======================================================================

Column {data-width=50}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

### Cronbach's alpha

```{r}
valueBox(round(Cronbach, digits = 2))
```

### Spearman-Brown alpha

```{r}
valueBox(round(SB, digits = 2))
```

### Kaiser-Caffrey alpha

```{r}
valueBox(round(KC, digits = 2))
```

### Average item corr.

```{r}
valueBox(round(AIC, digits = 2))
```


Column {data-width=200}
----------------------------------------------------------------------- 

### Reliability Analysis


**Central Tendency**

- Arithmetic mean (Mean)
- Median (Median)

**Dispersion**

- Standard deviation (St. dev.)
- Minimum (Min)
- Maximum (Max)
- Range (Range)

**Distribution**

- Skewness (Skew)
- Kurtosis (Kurt)
- Shapiro-Wilk test (W, p)
- Histogram
- Box & Whiskers plot

**Correlation**

- Correlation Matrix
- p - value
- Scatter Plot
- Correlation Network

**Reliability**

- Cronbach's alpha
- Spearman-Brown alpha
- Kaiser-Caffrey alpha


Column {data-width=750 .tabset}
-----------------------------------------------------------------------

### Data

```{r}
DT::datatable(data, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel')))
```

### Data Summary

```{r}
summary
```

### Z - values

```{r}
DT::datatable(Z, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(Z), digits=3)
```

### Condensed data

```{r}
DT::datatable (K_data, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(K_data), digits=3)
```

Descriptive Statistics
=======================================================================

Column {data-width=50}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

### Cronbach's alpha

```{r}
valueBox(round(Cronbach, digits = 2))
```

### Spearman-Brown alpha

```{r}
valueBox(round(SB, digits = 2))
```

### Kaiser-Caffrey alpha

```{r}
valueBox(round(KC, digits = 2))
```

### Average item corr.

```{r}
valueBox(round(AIC, digits = 2))
```


Column {data-width=450}
-----------------------------------------------------------------------

### Descriptive Statistics

```{r}
DT::datatable (ds, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy')))
```

Column {data-width=500}
-----------------------------------------------------------------------

### Graph Analysis

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
          radioButtons("radio", 
                       label = "Select Variable:",
                       choices = colnames(my_data)),
          
            sliderInput("bins",
                        "Broj razreda:",
                        min = 1,
                        max = 100,
                        value = 7)
        ),
        mainPanel(
          h4("Normality Test (Shapiro-Wilk)"),
          textOutput("shapiro"),
          hr(),
          h4("Histogram"),
          plotOutput("histogram"),
          hr(),
          h4("Box and Whiskers Plot"),
          plotOutput("box")
          )
),
server <- function(input, output, session) {

      selectedData <- reactive({
        my_data[, input$radio]
  })
     
      output$shapiro <- renderText({ 
        w <- selectedData()
        sw <- shapiro.test(w)
        W <- round(sw$statistic, digits = 3)
        p <- round(sw$p.value, digits = 3)
        paste("W = ", W,", p = ", p)
  })
      output$histogram <- renderPlot({
        x    <- selectedData()
        mean <- mean(selectedData())
        sd <- sd(selectedData())
        density <- dnorm(x=x, mean=mean(x), sd=sd(x)) 
        
        ggplot(my_data, aes(x=x)) + 
        geom_histogram(bins=input$bins, color="#ffffff", fill="#8ecae6") +
        geom_line(data=my_data, aes(y=density*n*(max(x)-min(x))/input$bins), colour="#e5e5e5", size=1) +
        labs(x= input$radio) +
        theme_minimal()
        
    })
      
       output$box <- renderPlot({
        Variables  <- selectedData()
        ggplot(my_data, aes(x=Variables, y=0)) + 
        geom_violin (fill='#8ecae6', color="#ffffff", alpha=0.7) +
        geom_boxplot(fill='#8ecae6', color="#ffffff",outlier.colour="red",outlier.shape=8, outlier.size=4) +
        labs(x = input$radio) +
        theme_minimal()
       })   
},
shinyApp(ui = ui, server = server)
)
```

Correlation Analysis
=======================================================================

Column {data-width=50}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

### Cronbach's alpha

```{r}
valueBox(round(Cronbach, digits = 2))
```

### Spearman-Brown alpha

```{r}
valueBox(round(SB, digits = 2))
```

### Kaiser-Caffrey alpha

```{r}
valueBox(round(KC, digits = 2))
```

### Average item corr.

```{r}
valueBox(round(AIC, digits = 2))
```

Column {data-width=450}
-----------------------------------------------------------------------

### Correlation Matrix

```{r}
DT::datatable (R, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(R), digits=2)
```

### p - value

```{r}
DT::datatable (P, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(P), digits=4)
```

Column {data-width=500}
-----------------------------------------------------------------------

### Scatter Plot

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
          radioButtons("xcol", 
                       label = "Select Variable x:",
                       choices = colnames(my_data)),
            radioButtons("ycol", 
                       label = "Select Variable y:",
                       choices = colnames(my_data)),
        ),
        mainPanel(
           h4("Scatter Plot"),
          plotOutput("scatter"),
   )
),
server <- function(input, output, session) {

      selectedData <- reactive({
        my_data[, c(input$xcol, input$ycol)]
  })
      output$scatter <- renderPlot({
        xx    <- selectedData()
        ggplot(xx, aes(x=xx[,1], y=xx[,2])) +
        geom_point(size=2, colour = "#145DA0") +
        labs(x= input$xcol, y = input$ycol) +
        theme_minimal()
    })
},
shinyApp(ui = ui, server = server)
)
```

### Correlation Network

```{r}

shinyApp(
  
ui <- fluidPage(
            sidebarPanel(
              sliderInput("r",
                        "Correlation Coefficient Level:",
                        min = 0,
                        max = 1,
                        value = 0.35),
     ),
        mainPanel(
           h4("Correlation Network"),
           plotOutput("corPlot")
       ),
),
server <- function(input, output) {
    output$corPlot <- renderPlot({
    my_data %>% correlate() %>% network_plot(min_cor=input$r)
    })
},
shinyApp(ui = ui, server = server)
)

```

