---
title: "Canonical Correlation Analysis"
output: 
  flexdashboard::flex_dashboard:
    #theme: bootstrap
    #theme: cerulean
    #theme: flatly
    #theme: united
    #theme: simplex
    theme: yeti
    logo: R_logo.png
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(DT)
library(psych)
library(nortest)
library(rstatix)
library(corrr)
library(skimr)
library(yacca)
library(ggthemes)
```

```{r Učitavanje podataka iz CSV datoteke}

#setwd("~/R-aplikacije/Datoteke/CSV")

data <- read.table(file.choose(),                  
                   header = TRUE,                      
                   dec = ",",                          
                   sep = ";",                          
                   stringsAsFactors = TRUE,
                   row.names = 1)
```

```{r Selekcija varijabli}

B1 <- data %>% select(VISI, TEZI, OBPO, NABN)
B2 <- data %>% select(TAPI, POLI, SDAL, POTR, PRRA, IZVI, TR6M)
```

```{r}
summary <- skim(data)
B <- cbind(B1, B2)
nvar1 <- colnames(B1)
nvar2 <- colnames(B2)
nvar <- colnames(B)
n <- nrow(data)                                  
m1 <- ncol(B1)
m2 <- ncol(B2)
m <- ncol(B)
if (m1<m2) {k=m1} else {k=m2}
```

```{r}
Z <- round(scale(B), digits = 2)
Z1 <- round(scale(B1), digits = 2)
Z2 <- round(scale(B2), digits = 2)
```

```{r}
R1 <- cor(B1)
R2 <- cor(B2)
RP <- corr.test(B)
R <- RP$r
P <- RP$p
```

```{r}
Rcnames <- c("Rc1", "Rc2","Rc3","Rc4","Rc5","Rc6","Rc7","Rc8","Rc9","Rc10","Rc11","Rc12","Rc13","Rc14","Rc15")
Rcn <- Rcnames[1:k]
rcca<- cca (B1, B2, xscale = TRUE, yscale = TRUE, standardize.scores = TRUE)
p <- pchisq(rcca$chisq, rcca$df,lower.tail = FALSE)
TRC <- cbind(round(rcca$corr, digits = 2), round(rcca$chisq, digits = 2), rcca$df, 
round(p,digits = 4))
colnames(TRC) <- c("Rc", "Chi-sq.","Df", "p-level")
TRC1 <- cbind.data.frame(Rcn,TRC)
```

```{r}
lamda1 <- eigen(R1)
lamda2 <- eigen(R2)
Eigenvalue1 <- lamda1$values
Eigenvalue2 <- lamda2$values
Eigenvectors1 <- lamda1$vectors
Eigenvectors2 <- lamda2$vectors
```

```{r}
K1 <- Z1 %*% Eigenvectors1
l1 <- sqrt(diag(Eigenvalue1,m1))                    
ZK1 <- K1 %*% solve(l1)                         

K2 <- Z2 %*% Eigenvectors2
l2 <- sqrt(diag(Eigenvalue2,m2))                    
ZK2 <- K2 %*% solve(l2) 
```

```{r}
if (m1>m2) {
   Q <- t(ZK1) %*% ZK2 /(n-1)
   QTQ <- t(Q) %*% Q
   RC2 <- eigen(QTQ)
   RC <- sqrt(RC2$values)
   Y2 <- RC2$vectors
   Y1 <- Q %*% Y2 %*% solve(diag(RC))
   CF1 <- ZK1 %*% Y1
   CF2 <- ZK2 %*% Y2
   F1 <- t(Z1) %*% CF1/ (n-1)
   F2 <- t(Z2) %*% CF2/ (n-1)
} else {
  Q <- t(ZK2) %*% ZK1 /(n-1)
  QTQ <- t(Q) %*% Q
  RC2 <- eigen(QTQ)
  RC <- sqrt(RC2$values)
  Y2 <- RC2$vectors
  Y1 <- Q %*% Y2 %*% solve(diag(RC))
  CF1 <- ZK1 %*% Y2
  CF2 <- ZK2 %*% Y1
  F1 <- (t(Z1) %*% CF1/ (n-1))
  F2 <- (t(Z2) %*% CF2/ (n-1))
} 

fnames <- c("CF1","CF2","CF3","CF4","CF5","CF6","CF7","CF8","CF9","CF10","CF11","CF12","CF13","CF14","CF15")
Faktori <- fnames[1:k]
colnames(CF1) <- fnames[1:k]
colnames(CF2) <- fnames[1:k]
colnames(F1) <- fnames[1:k]
colnames(F2) <- fnames[1:k]
```

```{r}
F1 <- round(F1, digits = 2)
F2 <- round(F2, digits = 2)
Fac1 <- rep(Faktori, each=m1)
Fac2 <- rep(Faktori, each=m2)
Var1 <- rep(nvar1, times=k)
Var2 <- rep(nvar2, times=k)
Loa1 <- c()
for (a in 1:k) {Loa1 <- c(Loa1,F1[,a])}
CFF1 <- data_frame(Fac1,Var1,Loa1)
Loa2 <- c()
for (a in 1:k) {Loa2 <- c(Loa2,F2[,a])}
CFF2 <- data_frame(Fac2,Var2,Loa2)
```

```{r}
GRCC <- ggplot(data=TRC1, aes(x=Rcn, y=Rc, fill=Rcn)) +
  geom_bar(stat="identity", color="#ffffff") +
  labs(x ="Canonical Correlations",y ="",title= "")+
  theme_minimal() + scale_fill_ptol()

GCF1 <- ggplot(data=CFF1, aes(x=Fac1,y=Loa1,fill=Var1)) +
  geom_bar(position ="stack",stat="identity") +
  labs(x ="Canonical factors",y ="Loadings",fill ="Variables",title= "")+
  theme_minimal() + scale_fill_ptol()

GCF2 <- ggplot(data=CFF2, aes(x = Fac2,y=Loa2 ,fill=Var2)) +
  geom_bar(position ="stack",stat="identity") +
  labs(x ="Canonical factors",y ="Loadings",fill ="Variables",title= "")+
  theme_minimal() + scale_fill_ptol()
```

Data
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables First Set

```{r}
valueBox(m1)
```

### Variables Second Set

```{r}
valueBox(m2)
```

### Data

```{r}
valueBox(n*(m1+m2))
```


Column {data-width=640 .tabset}
-----------------------------------------------------------------------

### Data

```{r}
DT::datatable(data, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel')))
```

### Data Summary

```{r}
summary
```

### Z - values

```{r}
DT::datatable(Z, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel')))
```

Column {data-width=350 .tabset}
-----------------------------------------------------------------------

### Canonical Factors - First Set

```{r}
DT::datatable(CF1, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(CF1), digits=2)
```

### Canonical Factors - Second Set

```{r}
DT::datatable(CF2, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(CF2), digits=2)
```


Descirptive Statistics
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables First Set

```{r}
valueBox(m1)
```

### Variables Second Set

```{r}
valueBox(m2)
```

### Data

```{r}
valueBox(n*(m1+m2))
```

Column {data-width=990 .tabset}
-----------------------------------------------------------------------

### Descirptive Parameters

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
         checkboxGroupInput("select_vars", "Select Variables:",
                            names(B), selected = names(B)),
        ),
        mainPanel(
          dataTableOutput("desc"),
          hr(),
           h5("Legend:"),
           h6("- Arithmetic mean (MEAN)"),
           h6("- Median (MEDIAN)"),
           h6("- Standard deviation (SD)"),
           h6("- Coefficient of Variation (CV)"),
           h6("- Minimum (MIN)"),
           h6("- Maximum (MAX)"),
           h6("- Range (RANGE)"),
           h6("- Skewness (SKEW)"),
           h6("- Kurtosis (KURT)"),
           h6("- Standard error of the mean (SEM)"),
          )
),

server <- function(input, output, session) {

  selectedData <- reactive({
    data[, input$select_vars]
  })
    
  output$desc <- renderDataTable({
    my_data <- selectedData()
    dp <- describe(my_data, type=3)
    kv <- dp$sd/dp$mean*100
    dp <- cbind(dp,kv)
    dp <- dp[c(3, 5, 4, 14, 8, 9, 10, 11, 12, 13)]
    colnames(dp) <- c("MEAN", "MEDIAN", "SD", "CV", "MIN", "MAX", "RANGE", "SKEW", "KURT", "SEM")
    dp <- round(dp, digits = 3)
    dp %>% DT::datatable (rownames = TRUE, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy')))
  })
  
},

shinyApp(ui = ui, server = server)
)
```

### Testing for Normality 

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
          radioButtons("radio", 
                       label = "Select Variable:",
                       choices = colnames(B)),
          
            sliderInput("bins",
                        "Number of Bins:",
                        min = 1,
                        max = 100,
                        value = 7)
        ),
        mainPanel(
          h4("Normality Test"),
          textOutput("ks"),
          textOutput("lks"),
          textOutput("ad"),
          textOutput("sf"),
          textOutput("sw"),
          hr(),
          h4("Histogram"),
          plotOutput("histogram"),
          hr(),
          h4("Box and Whiskers Plot"),
          plotOutput("box"),
          hr(),
          h4("Q-Q Plot"),
          plotOutput("qq")
          )
),
server <- function(input, output, session) {

      selectedData <- reactive({
        B[, input$radio]
  })
      output$ks <- renderText({ 
        x <- selectedData()
        ks <- ks.test(x, "pnorm", mean=mean(x), sd=sd(x))
        D <- round(ks[["statistic"]][["D"]], digits = 3)
        pks <- round(ks[["p.value"]], digits = 3)
        paste("Kolmogorov-Smirnov test:", "D = ", D,", p = ", pks)
  })       
      output$lks <- renderText({ 
        x <- selectedData()
        lt <- lillie.test(x)
        Dlks <- round(lt[["statistic"]][["D"]], digits = 3)
        plks <- round(lt[["p.value"]], digits = 3)
        paste("Lilliefors test:", "D = ", Dlks,", p = ", plks)
  })   
      output$ad <- renderText({ 
        x <- selectedData()
        ad <- ad.test(x)
        A <- round(ad[["statistic"]][["A"]], digits = 3)
        pa <- round(ad[["p.value"]], digits = 3)
        paste("Anderson-Darling test:", "A = ", A,", p = ", pa)
  })   
      output$sf <- renderText({ 
        x <- selectedData()
        sf <- sf.test(x)
        Wsf <- round(sf[["statistic"]][["W"]], digits = 3)
        psf <- round(sf[["p.value"]], digits = 3)
        paste("Shapiro-Francia test:", "W = ", Wsf,", p = ", psf)
  }) 
      output$sw <- renderText({ 
        x <- selectedData()
        sw <- shapiro.test(x)
        W <- round(sw$statistic, digits = 3)
        psw <- round(sw$p.value, digits = 3)
        paste("Shapiro-Wilk test:", "W = ", W,", p = ", psw)
        
  })
      output$histogram <- renderPlot({
        x <- selectedData()
        ggplot(B, aes(x=x)) + 
        geom_histogram(bins=input$bins, color="#000000", fill="#5BC0DE") +
        labs(x= input$radio) +
        theme_minimal()
       })
      
       output$box <- renderPlot({
        x <- selectedData()
         ggplot(B, aes(x=x, y=0)) +
         geom_boxplot(fill='#5BC0DE', outlier.colour="#d64045", outlier.shape=8, outlier.size=2) +
         labs(x = input$radio) +
         theme_minimal()
       })   
       
       output$qq <- renderPlot({
        x <- selectedData()
        ggplot(B, aes(sample = x)) + 
        stat_qq_line(color="#000000",size=1) + 
        stat_qq(color="#145DA0", size=2) + 
        labs(x = input$radio, y=input$radio) +
        theme_minimal()
       }) 
        
},
shinyApp(ui = ui, server = server)
)
```

Correlation Analysis
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables First Set

```{r}
valueBox(m1)
```

### Variables Second Set

```{r}
valueBox(m2)
```

### Data

```{r}
valueBox(n*(m1+m2))
```


Column {data-width=990 .tabset}
-----------------------------------------------------------------------

### Correlation Analysis

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
         checkboxGroupInput("select_vars", "Select Variables:",
                            names(B), selected = names(B)),
         
         radioButtons("method", "Method:",
                   choices = c(Pearson = "pearson",
                               Spearman = "spearman",
                               Kendall = "kendall"),
                   selected = "pearson"),

        ),
        mainPanel(
          h4("Correlation Matrix"),
          dataTableOutput("r"),
            hr(),
          h4("p - value"),
          dataTableOutput("p"),
          )
),

server <- function(input, output, session) {

  selectedData <- reactive({
    data[, input$select_vars]
  })
    
  output$r <- renderDataTable({
    my_data <- selectedData()
    var_name_numeric <- names(my_data)
    RP <- corr.test(my_data, method = input$method)
    R <- RP$r
    R %>% DT::datatable (rownames = TRUE, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(R), digits=2)
   })
  
   output$p <- renderDataTable({
    my_data <- selectedData()
    var_name_numeric <- names(my_data)
    RP <- corr.test(my_data, method = input$method)
    P <- RP$p
    P %>% DT::datatable (rownames = TRUE, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(P), digits=4) %>% formatStyle(var_name_numeric, color = styleInterval(c(0.05), c('red', 'black')))
  })
  
},

shinyApp(ui = ui, server = server)
)
```

### Scatter Plot

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
          radioButtons("xcol", 
                       label = "Select Variable x:",
                       choices = colnames(B)),
            radioButtons("ycol", 
                       label = "Select Variable y:",
                       choices = colnames(B)),
        ),
        mainPanel(
          h4("Scatter Plot"),
          plotOutput("scatter"),
            hr(),
          h4("Correlation Coefficients"),
          htmlOutput("r"),
   )
),
server <- function(input, output, session) {

      selectedData <- reactive({
        B[, c(input$xcol, input$ycol)]
        
  })
      output$scatter <- renderPlot({
        xx  <- selectedData()
        ggplot(xx, aes(x=xx[,1], y=xx[,2])) +
        geom_point(size=2, colour = "#145DA0") +
        geom_smooth(method = "lm", colour = "#d64045", size=1, se = F) +
        labs(x= input$xcol, y = input$ycol) +
        theme_minimal()
    })
      
      output$r <- renderText({ 
        xx <- selectedData()
        x <- xx[,1]
        y <- xx[,2]
        r <- round(cor(x, y, method = "pearson"), digits = 2)
        rho <- round(cor(x, y, method = "spearman"), digits = 2)
        tau <- round(cor(x, y, method = "kendall"), digits = 2)
        pr <- cor.test(x, y, method = "pearson")
        pr <- round(pr$p.value, digits = 3)
        prho <- cor.test(x, y, method = "spearman")
        prho <- round(prho$p.value, digits = 3)
        ptau <- cor.test(x, y, method = "kendall")
        ptau <- round(ptau$p.value, digits = 3)
        paste(
              "Pearson r = " , r, ", p =", pr, "</br>",
              "Spearman rho = ", rho, ", p =", prho, "</br>",
              "Kendell tau = ", tau, ", p =", ptau
              )
  })
},
shinyApp(ui = ui, server = server)
)
```

### Correlation Network

```{r}

shinyApp(
  
ui <- fluidPage(
            sidebarPanel(
              checkboxGroupInput("select_vars", "Select Variables:",
                            names(B), selected = names(B)),
              sliderInput("r",
                        "Correlation Coefficient Level:",
                        min = 0,
                        max = 1,
                        value = 0.35),
     ),
        mainPanel(
           h4("Correlation Network"),
           plotOutput("corPlot")
       ),
),
server <- function(input, output, session) {
  
    selectedData <- reactive({
    data[, input$select_vars]
  })    
  
    output$corPlot <- renderPlot({
    my_data <- selectedData()
    my_data %>% correlate() %>% network_plot(min_cor=input$r)
    })
},
shinyApp(ui = ui, server = server)
)

```

Canonical Correlation Analysis
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables First Set

```{r}
valueBox(m1)
```

### Variables Second Set

```{r}
valueBox(m2)
```

### Data

```{r}
valueBox(n*(m1+m2))
```


Column {data-width=270}
-----------------------------------------------------------------------

### Canonical Correlations

```{r}
DT::datatable (TRC, rownames=FALSE, extensions = 'Buttons', options = list(pageLength = k, dom = 'Bt',buttons = c('copy'))) %>% formatStyle("p-level", color = styleInterval(c(0.05), c('red', 'black')))
```

### Graph of Canonical Correlations

```{r}
GRCC
```

Column {data-width=365}
-----------------------------------------------------------------------

### Canonical Loadings First Set

```{r}
DT::datatable (F1, extensions = 'Buttons', options = list(pageLength = m1, dom = 'Bt',buttons = c('copy')))

```

### Graph of Canonical Loadings First Set

```{r}
GCF1
```


Column {data-width=365}
-----------------------------------------------------------------------

### Canonical Loadings Second Set

```{r}
DT::datatable (F2, extensions = 'Buttons', options = list(pageLength = m2, dom = 'Bt',buttons = c('copy')))
```

### Graph of Canonical Loadings Second Set

```{r}
GCF2
```

