---
title: "Metric Characteristics"
output: 
  flexdashboard::flex_dashboard:
    #theme: bootstrap
    #theme: cerulean
    #theme: flatly
    #theme: united
    #theme: simplex
    theme: yeti
    logo: R_logo.png
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(DT)
library(psych)
library(rstatix)
library(corrr)
library(tigerstats)
library(skimr)
library(irr)
```

```{r Učitavanje podataka iz CSV datoteke}

data <- read.table(file.choose(),                  
                   header = TRUE,                      
                   dec = ",",                          
                   sep = ";",                          
                   stringsAsFactors = TRUE,
                   row.names = 1)

#saveRDS(data, file = "MUHCS20m.RData") 
#head(data)
```

```{r Selekcija varijabli}
#my_data <- data %>% select_if(is.numeric)

my_data <- data %>% select(FEDSM1, FEDSM2, FEDSM3)
#my_data <- data %>% select(BFPTAP1, BFPTAP2, BFPTAP3)
#my_data <- data %>% select(FLPRR1,	FLPRR2,	FLPRR3)
#my_data <- data %>% select(AGKUS1, AGKUS2, AGKUS3)
```

```{r}
n <- nrow(my_data)                                  
m <- ncol(my_data)
varijable <- names(my_data)
summary <- skim(data)
Z <- round(scale(my_data), digits = 3)
```

```{r}
X <- as.matrix(my_data)                    
i <- rep(c(1), times=m)                     
Xs <- X %*% i                               
Xas <- Xs/m                                 
colnames(Xs) <- c("X-sum")
colnames(Xas) <- c("X-mean")
Xas <- as.data.frame(Xas)
```

```{r}
Zm <- as.matrix(Z)                    
Zs <- Zm %*% i                               
Zas <- Zs/m                                 
colnames(Zs) <- c("Z-sum")
colnames(Zas) <- c("Z-mean")
Zas <- as.data.frame(Zas)
```

```{r}
k <- principal(X, nfactors=1, scores=TRUE) 

lamda_values <- c(k$values[k$values>=1])
g <- length(lamda_values)
load <- round(k[["loadings"]][], digits = 2)
lamdaR1 <- k$values[1]                         
K1 <- k$scores
K1<- as.data.frame(K1)
```

```{r}
ds <- describe(my_data, type=3)
ds <- ds[c(3,5,4,8,9,10,11,12)]
colnames(ds) <- c("Mean", "Median", "St.dev", "Min", "Max", "Range", "Skew", "Kurt")
ds <- round(ds, digits = 3)
```

```{r}
RP <- corr.test(my_data)
R <- RP$r
P <- RP$p

invR <- solve(R)
diaginvR <- diag(invR)
U2 <- solve(diag(diaginvR))
I <- diag(1, m)
i <- diag(I)
SMC <- I - U2
U <- sqrt(U2)
invU <- solve(U)
H <- Z %*% invU

CA <- U2 %*% invR %*% U2
CG <- R + (U2 %*% invR %*% U2) - 2*U2
CH <-  invU %*% R %*% invU

lamdaG <- eigen(CG)
lamdaH <- eigen(CH)

lamdaG1 <- lamdaG$values[1]
lamdaH1 <- lamdaH$values[1]

LAMDA6 <- 1-1/lamdaH1
RHO1 <- (1-(1/lamdaH1))**2
RHO2 <- 1-1/lamdaH1**2

TAU <- lamdaG1/lamdaR1

MSA1 <- t(i) %*% ((CA-U2)*(CA-U2)) %*% i
MSA2 <- t(i) %*% ((R-U2)*(R-U2)) %*% i
MSA <- 1-(MSA1/MSA2)
HOM1 <- 1-(g-1)/(m-1)
HOM2 <- lamdaG1/sum(diag(CG))

```

```{r}
svar <- sum(ds[,3]*ds[,3]) 
varXs <- var(Xs)                             
varZs <- var(Zs)                             

Cronbach <- m/(m-1)*(1-svar/varXs)             
SB <- m/(m-1)*(1-m/varZs)                
KC <- m/(m-1)*(1-1/lamdaR1)               
k <- (m*m-m)/2                              
AIC<- c((sum(R)-m)/2)/k
K_data <- cbind.data.frame(Xas, Zas, K1)
```

```{r}
alp <- alpha(my_data)
is1 <- alp$item.stats
is2 <- alp$alpha.drop
is <- cbind(is1, is2)
is <- is[c(1,6,7,5,8)]
colnames(is) <- c("N", "Mean", "St.dev.", "Corr. if deleted", "Alpha if deleted")
is <- round(is, digits = 3)
```


Data
=======================================================================

Column {data-width=50}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

Column {data-width=390}
----------------------------------------------------------------------- 

### Metric Characteristics of Measuring Instruments


**Central Tendency**

- Arithmetic mean (Mean)
- Median (Median)

**Dispersion**

- Standard deviation (St. dev.)
- Minimum (Min)
- Maximum (Max)
- Range (Range)

**Distribution**

- Skewness (Skew)
- Kurtosis (Kurt)
- Shapiro-Wilk test (W, p)
- Histogram
- Box & Whiskers plot

**Correlation**

- Correlation Matrix
- p - value

**Metric Characteristics**

- Intraclass Correlation (ICC)
- Cronbach's alpha (Cronbach's)
- Spearman-Brown alpha (Spearman-Brown)
- Kaiser-Caffrey alpha (Kaiser-Caffrey)
- Guttman-Nicewanderova (Lamda 6)
- Lower Reliability Limit (Rho 1)
- Upper Reliability Limit (Rho 2)
- Momirovic's Lower Reliability Limit (Tau)
- Kaiser - Rice representativeness coefficient (MSA)
- Measure of homogeneity based on the number of principal components whose variance is greater than or equal to 1 (Hom 1)
- Momirović's homogeneity coefficient (Hom 2)
- Item-Total Statistics
- Internal Validity

Column {data-width=600 .tabset}
-----------------------------------------------------------------------

### Data

```{r}
DT::datatable(data, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel')))
```

### Data Summary

```{r}
summary
```

### Z - values

```{r}
DT::datatable(Z, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(Z), digits=3)
```

### Condensed data

```{r}
DT::datatable (K_data, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(K_data), digits=3)
```

Descriptive Statistics
=======================================================================

Column {data-width=50}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```


Column {data-width=450}
-----------------------------------------------------------------------

### Descriptive Statistics

```{r}
DT::datatable (ds, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy')))
```

Column {data-width=500}
-----------------------------------------------------------------------

### Graph Analysis

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
          radioButtons("radio", 
                       label = "Select Variable:",
                       choices = colnames(my_data)),
          
            sliderInput("bins",
                        "Broj razreda:",
                        min = 1,
                        max = 100,
                        value = 7)
        ),
        mainPanel(
          h4("Normality Test (Shapiro-Wilk)"),
          textOutput("shapiro"),
          hr(),
          h4("Histogram"),
          plotOutput("histogram"),
          hr(),
          h4("Box and Whiskers Plot"),
          plotOutput("box")
          )
),
server <- function(input, output, session) {

      selectedData <- reactive({
        my_data[, input$radio]
  })
     
      output$shapiro <- renderText({ 
        w <- selectedData()
        sw <- shapiro.test(w)
        W <- round(sw$statistic, digits = 3)
        p <- round(sw$p.value, digits = 3)
        paste("W = ", W,", p = ", p)
  })
      
       output$histogram <- renderPlot({
        x <- selectedData()
        ggplot(my_data, aes(x=x)) + 
        geom_histogram(bins=input$bins, color="#000000", fill="#8ecae6") +
        labs(x= input$radio) +
        theme_minimal()
       })
      
       output$box <- renderPlot({
        x <- selectedData()
         ggplot(my_data, aes(x=x, y=0)) +
         geom_boxplot(fill='#8ecae6', outlier.colour="#d64045", outlier.shape=16, outlier.size=2) +
         labs(x = input$radio) +
         theme_minimal()
       })   
},
shinyApp(ui = ui, server = server)
)
```

Metric Characteristics
=======================================================================

Column {data-width=50}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

Column {data-width=450}
-----------------------------------------------------------------------

### Correlation Matrix

```{r}
DT::datatable (R, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(R), digits=2)
```

### p - value

```{r}
DT::datatable (P, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(P), digits=4) %>% formatStyle(varijable, color = styleInterval(c(0.05), c('red', 'black')))
```

Column {data-width=500}
-----------------------------------------------------------------------

### Metric Characteristics of Measuring Instruments

```{r}
shinyApp(

ui <- fluidPage(h4("Intraclass Correlation"),
      radioButtons("model", "Model:",
                   c("Oneway" = "one",
                     "Twoway" = "two")),
      radioButtons("type", "Type:",
                   c("Consistency" = "con",
                     "Agreement" = "agr")),
      radioButtons("unit", "Unit:",
                   c("Average" = "ave",
                     "Single" = "sin")),
        
        mainPanel(
           htmlOutput("icc"),
            hr(),
           h4("Reliability"),
           h5("Cronbach's = ", round(Cronbach, digits = 2)),
           h5("Spearman-Brown = ", round(SB, digits = 2)), 
           h5("Kaiser-Caffrey = ", round(KC, digits = 2)), 
           h5("Lamda 6 = ", round(LAMDA6, digits = 2)),
           h5("Rho 1 = ", round(RHO1, digits = 2)), 
           h5("Rho 2 = ", round(RHO2, digits = 2)), 
           h5("Tau = ", round(TAU, digits = 2)),
            hr(),
           h4("Homogeneity"),
           h5("Hom 1 = ", round(HOM1, digits = 2)),
           h5("Hom 2 = ", round(HOM2, digits = 2)), 
           h5("Average item corr. =", round(AIC, digits = 2)),
           hr(),
           h5("MSA = ", round(MSA, digits = 2)), 
            hr(),
           h4("Item-Total Statistics"),
           dataTableOutput("is"),
            hr(),
           h4("Internal Validity"),
           dataTableOutput("load"),
            hr(),
           h5("Legend:"),
           h6("Cronbach's - Cronbachov koeficijent pouzdanosti (Cronbach, 1951)"),
           h6("Spearman-Brown - Spearman-Brownov koeficijent pouzdanosti"),
           h6("Kaiser-Caffrey - Kaiser-Caffreyev koeficijent pouzdanosti (Kaiser i Caffrey, 1965)"),
           h6("Lamda 6 - Guttman-Nicewanderova koeficijent pouzdanosti (Nicewander, 1975.)"),
           h6("Rho 1 - donja granica pouzdanosti  (Momirović, Dobrić, 1976.)"),
           h6("Rho 2 - gornja granica pouzdanosti (Zakrajšek, Momirović, Dobrić, 1977.)"),
           h6("Tau - Momirovićeva donja granica pouzdanosti (Momirović, 1975.)"),
           h6("MSA - Kaiser - Riceov koeficijent reprezentativnost (Kaiser, Rice, 1974.)",
           h6("Hom 1 - Mjera homogenosti  koja se temelji na broju glavnih komponenata čija je varijanca veća ili jednaka 1 (Momirović i Gredelj, 1980)"),
           h6("Hom 2 - Momirovićev koeficijent homogenosti (Momirović, 1977.)")),
           hr(),

   )
),
server <- function(input, output, session) {
  
 output$icc <- renderText({
    icc <- icc(my_data, 
            model = input$model,
            type  = input$type,
            unit  = input$unit, 
            r0 = 0, 
            conf.level = 0.95)
            paste(
              "Intraclass Corr. Coeff. (ICC) = ", round(icc$value, digits = 2), "; F-value =", round(icc$Fvalue, digits = 2), "; p - value = ",    round(icc$p.value, digits = 3), "</br>",
              "95% Conf. Interval for ICC =", round(icc$lbound,digits = 2),  " ~ ", round(icc$ubound, digits = 2)
              )
   })
  output$is <- renderDataTable({
    is%>% DT::datatable (rownames = TRUE, extensions = 'Buttons', options = list(pageLength = 100, dom = 'Bt',buttons = c('copy')))
 })
 
 output$load <- renderDataTable({
    load%>% DT::datatable (rownames = TRUE, extensions = 'Buttons', options = list(pageLength = 100, dom = 'Bt',buttons = c('copy')))
 })
 
},
shinyApp(ui = ui, server = server)
)
```
