---
title: "Regression Analysis"
output: 
  flexdashboard::flex_dashboard:
    #theme: bootstrap
    #theme: cerulean
    #theme: flatly
    #theme: united
    #theme: simplex
    theme: yeti
    logo: R_logo.png
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(DT)
library(psych)
library(rstatix)
library(corrr)
library(tigerstats)
library(skimr)
```

```{r Učitavanje podataka iz CSV datoteke}

#setwd("~/R-aplikacije/Datoteke/CSV")

data <- read.table(file.choose(),                  
                   header = TRUE,                      
                   dec = ",",                          
                   sep = ";",                          
                   stringsAsFactors = TRUE,
                   row.names = 1)

#saveRDS(data, file = "JUDO3F.RData") 
#head(data)
```

```{r Selekcija varijabli}

#Odabir varijabli rednim brojem varijable

#Independent <- data %>% select(c(1,2,3,4,5,6,7,8,9,10))
#Dependent <- data %>% select(c(11))

#Odabir varijabli nazivom varijable

Independent <- data %>% select(VISI, TEZI, OBPO, NABN, TAPI,	POLI, SDAL, POTR,	PRRA, IZVI)
Dependent <- data %>% select(TR6M)  
```

```{r}
my_data <- cbind(Independent, Dependent)
nvar <- colnames(my_data)
n <- nrow(my_data)
m <- ncol(my_data)
summary <- skim(data)
```

```{r}
X <- as.matrix(Independent)
Y <- as.matrix(Dependent)
XY <- cbind(X,Y)
Variables <- colnames(X)
nvarY <- colnames(Y)
```

```{r}
ds <- describe(my_data, type=2)
ds <- ds[c(3,5,4,8,9,10,11,12)]
colnames(ds) <- c("Mean", "Median", "St.dev", "Min", "Max", "Range", "Skew", "Kurt")
ds <- round(ds, digits = 2)
```

```{r}
Z <- scale(X)
K <- scale(Y)
ZK <- round(cbind(Z,K), digits = 2)
```

```{r}
RP <- corr.test(my_data)
Rxy <- RP$r
P <- RP$p
R <- cor(X)
```

```{r}
B0 <- rep.int(1, n)
Xi <- cbind(B0,X)
XTXi <- t(Xi) %*% Xi
XTY <- t(Xi) %*% Y
b <- solve(XTXi) %*% XTY
```

```{r}
r1 <- (t(Z) %*% K)/(n-1)
r <- rbind(0, r1)
beta1 <- solve(R) %*% r1
beta <- rbind(0,beta1)
```

```{r}
S2 <- 1/diag(solve(R))
#S <- sqrt(S2)
s2 <- data.frame(S2)
s2<- rbind(0,s2)
S2xy <- 1/diag(solve(Rxy))
Sxy <- sqrt(S2xy)

Pr <- diag(Sxy) %*% solve(Rxy) %*% diag(Sxy)
pr <- (Pr[,m]*-1)
pr <- pr[1:m-1]
pr <- data.frame(pr)
pr <- rbind(0,pr)
p <- beta*r
```

```{r}
j <- rep.int(1, m)
ro2 <- t(p)%*%j
ro <- round(sqrt(ro2), digits = 2)
```

```{r}
Yp <- Xi %*% b 
e <- Y - Yp
```

```{r}
se <- round(sqrt(sum(e*e)/(n-m)), digits = 2)
wjj <- solve(XTXi)
diagwjj <- diag(wjj)
seb <- se*sqrt(diagwjj)
tb <- abs(b/seb)
df <- n-m
pval <- c()
for (a in 0:m) {pval[a] <- c(2*(pt(abs(tb[a,1]), df, lower.tail = FALSE)))}
tb <- data.frame(tb)
pval <- data.frame(pval)
```

```{r}
REZULTATI <- round(cbind(b, seb, beta, pr, r, p, s2, tb, pval), digits = 3)
colnames(REZULTATI) <- c("B","SE(B)", "Beta", "Part_R", "R","P", "Tolerance", "t-value", "p-value")
```

```{r}
pss <- sum((Yp-mean(Yp))**2)
rss <- sum((e-mean(e))**2)
dfp <- m-1
dfe <- n-m
Fval <- (pss/dfp)/(rss/dfe)
pf <- round(pf(Fval, dfp, dfe, lower.tail = FALSE), digits = 3)
rez_ro <- c(ro, se, Fval, pf)
rez_ro <- data.frame(t(rez_ro))
colnames(rez_ro) <- c("RO", "SEE", "F", "p-value")
```

```{r}
pgg <- round(p[2:m], digits = 2)
pggdf <- cbind.data.frame(Variables,pgg)

gro <- ggplot(pggdf, aes(x= Variables, y = pgg, fill = Variables)) +
       geom_bar(stat = "identity", color = "white") +
       labs(x ="Variables",y ="value",fill ="",title= "")+
       theme_minimal()

grez <- cbind.data.frame(Variables,REZULTATI$Beta[2:m], REZULTATI$Part_R[2:m], REZULTATI$R[2:m])
ncoef <- c("BETA", "PART-R", "R")
coef <- rep(ncoef, each=m-1)
var <- rep(Variables, times=3)
val <- c()
for (a in 2:4) {val <- c(val,grez[,a])}
ggrez <- data_frame(coef,var,val)

gcoef <- ggplot(ggrez, aes(x=var, y = val, fill= coef)) +
         geom_bar(position="dodge",stat = "identity")+
         labs(x ="Variables",y ="value",fill ="",title= "")+
         theme_minimal()
```

Data
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```


Column {data-width=800 .tabset}
-----------------------------------------------------------------------

### Data

```{r}
DT::datatable(data, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel')))
```

### Data Summary

```{r}
summary
```

### Z - values

```{r}
DT::datatable(ZK, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel')))
```

Column {data-width=200 .tabset}
-----------------------------------------------------------------------

### Predicted Values

```{r}
DT::datatable(Yp, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(Yp), digits=2)
```

### Residual Values

```{r}
DT::datatable(e, extensions = 'Buttons', options = list(pageLength = n, dom = 'Bfrtip',buttons = c('copy','csv', 'excel'))) %>% formatRound(colnames(e), digits=2)
```

Descriptive Statistics
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

Column {data-width=390}
-----------------------------------------------------------------------

### Descriptive Statistics

```{r}
DT::datatable (ds, extensions = 'Buttons', options = list(pageLength = m, dom = 'Bt',buttons = c('copy')))
```

Column {data-width=600}
-----------------------------------------------------------------------

### Graph Analysis

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
          radioButtons("radio", 
                       label = "Select Variable:",
                       choices = colnames(my_data)),
          
            sliderInput("bins",
                        "Broj razreda:",
                        min = 1,
                        max = 100,
                        value = 7)
        ),
        mainPanel(
          h4("Normality Test (Shapiro-Wilk)"),
          textOutput("shapiro"),
          hr(),
          h4("Histogram"),
          plotOutput("histogram"),
          hr(),
          h4("Box and Whiskers Plot"),
          plotOutput("box")
          )
),
server <- function(input, output, session) {

      selectedData <- reactive({
        my_data[, input$radio]
  })
     
      output$shapiro <- renderText({ 
        w <- selectedData()
        sw <- shapiro.test(w)
        W <- round(sw$statistic, digits = 3)
        p <- round(sw$p.value, digits = 3)
        paste("W = ", W,", p = ", p)
  })
      output$histogram <- renderPlot({
        x    <- selectedData()
        mean <- mean(selectedData())
        sd <- sd(selectedData())
        density <- dnorm(x=x, mean=mean(x), sd=sd(x)) 
        
        ggplot(my_data, aes(x=x)) + 
        geom_histogram(bins=input$bins, color="#ffffff", fill="#8ecae6") +
        geom_line(data=my_data, aes(y=density*n*(max(x)-min(x))/input$bins), colour="#e5e5e5", size=1) +
        labs(x= input$radio) +
        theme_minimal()
        
    })
      
       output$box <- renderPlot({
        Variables  <- selectedData()
        ggplot(my_data, aes(x=Variables, y=0)) + 
        geom_violin (fill='#8ecae6', color="#ffffff", alpha=0.7) +
        geom_boxplot(fill='#8ecae6', color="#ffffff",outlier.colour="red",outlier.shape=8, outlier.size=4) +
        labs(x = input$radio) +
        theme_minimal()
       })   
},
shinyApp(ui = ui, server = server)
)
```

Correlation Analysis
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

Column {data-width=490}
-----------------------------------------------------------------------

### Correlation Matrix

```{r}
DT::datatable (Rxy, extensions = 'Buttons', options = list(pageLength = m+1, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(Rxy), digits=2)
```

### p - value

```{r}
DT::datatable (P, extensions = 'Buttons', options = list(pageLength = m+1, dom = 'Bt',buttons = c('copy'))) %>% formatRound(colnames(P), digits=4) %>% formatStyle(nvar, color = styleInterval(c(0.05), c('red', 'black')))
```

Column {data-width=500}
-----------------------------------------------------------------------

### Scatter Plot

```{r}
shinyApp(

ui <- fluidPage(
        sidebarPanel(
          radioButtons("xcol", 
                       label = "Select Variable x:",
                       choices = colnames(my_data)),
            radioButtons("ycol", 
                       label = "Select Variable y:",
                       choices = colnames(my_data)),
        ),
        mainPanel(
           h4("Scatter Plot"),
          plotOutput("scatter"),
   )
),
server <- function(input, output, session) {

      selectedData <- reactive({
        my_data[, c(input$xcol, input$ycol)]
  })
      output$scatter <- renderPlot({
        xx    <- selectedData()
        ggplot(xx, aes(x=xx[,1], y=xx[,2])) +
        geom_point(size=2, colour = "#145DA0") +
        labs(x= input$xcol, y = input$ycol) +
        theme_minimal()
    })
},
shinyApp(ui = ui, server = server)
)
```

### Correlation Network

```{r}

shinyApp(
  
ui <- fluidPage(
            sidebarPanel(
              sliderInput("r",
                        "Correlation Coefficient Level:",
                        min = 0,
                        max = 1,
                        value = 0.35),
     ),
        mainPanel(
           h4("Correlation Network"),
           plotOutput("corPlot")
       ),
),
server <- function(input, output) {
    output$corPlot <- renderPlot({
    my_data %>% correlate() %>% network_plot(min_cor=input$r)
    })
},
shinyApp(ui = ui, server = server)
)

```

Regression Analysis
=======================================================================

Column {data-width=10}
-----------------------------------------------------------------------

### Cases

```{r}
valueBox(n)
```

### Variables

```{r}
valueBox(m)
```

### Data

```{r}
valueBox(n*m)
```

### Multiple Correlation

```{r}
valueBox(ro,color="danger")
```

### Coefficient of Determination

```{r}
ro2 <- round(ro2, digits = 2)
valueBox(ro2, color="danger")
```

### Standard Error of the Estimate

```{r}
valueBox(se, color="danger")
```

### F - value

```{r}
valueBox(round(Fval, digits = 2), color="danger")
```

### p - level

```{r}
valueBox(round(pf, digits = 3), color="danger")
```

Column {data-width=500}
-----------------------------------------------------------------------

### Results of Regression Analysis

```{r}
DT::datatable (REZULTATI, extensions = 'Buttons', options = list(pageLength = m+1, dom = 'Bt',buttons = c('copy')))  %>% formatRound(colnames(REZULTATI), digits=3) %>% formatStyle('p-value', color = styleInterval(c(0.05), c('red', 'black')))
```


Column {data-width=500}
-----------------------------------------------------------------------

### Graph of Partial Coefficient of Determinations (P)

```{r}
gro
```


### Graph of Standardized Regression Coefficients, Partial Correlations and Correlations

```{r}
gcoef
```

